Background Music Will not Significantly Distract Attention

### 2021-04-25 Output/paper/paper.Rmd
update discussion

### The enjoyment of music will affect the completion time of the test
After completing two rounds of testing, participants were asked to rate the background music, 1 to 5 anonymously. The higher the score, represents the more they liked the song. From the results, when the participants give a score greater than or equal to 3, the average time to complete the test is less than the overall average completion time. This shows that when people hear the background music they don’t like, their attention level is much lower than those who listen to background music they like.

@@

### Each student’s initial attention level is different
When checking linear mixed model validation, the resulting plot shows that there exist random intercepts and random slopes, which illustrates that each students' initial attention level is different and fixed effects will vary for each student. In other words, the linear mixed model is suitable for this data and can incorporate student-to-student variability in finishing time and improve the ability to describe how fixed effects relate to outcomes.

### Background music does not significantly affect the level of attention of students
Although in the descriptive analysis, it is found that in the case of background music, the average time for students to complete the test is longer than that without background music. But in the process of comparing the five models, the results show that test_type is not significant among all the models. This shows that it fails to prove that background music will affect the level of attention of students in a statistical sense.

### The order of testing will affect the time to complete the test
When comparing models, the results show that the order significantly affects the time it takes for students to complete the test. In the final best-fit model, the coefficient of order is -10.65, and the 90% confidence interval is from -14.85 to -6.45. The coefficient, -10.65, means, on average, the time for completing the test in second-order is 10.65 seconds faster than the time in the first order when holding other variables constant.

@@

## Weaknesses and Next Steps
### Weaknesses

**Practice Effect:**
Each participant is measured for two conditions in the within-subject design(repeated measure design). Participants learn about the type and difficulty of the question when they take the Trail Making Test for the first time, so they may become more adept simply with the question and more proficient because of the repeated test, making the second-round test result more optimistic. In addition to the students' understanding of the test questions, some participants may feel bored or have a negative attitude to repeat the same test, making the results inaccurate.

**Hawthorn Effect:**
During the experiment, participants know that they are part of the experiment and observed. Their speed of doing the tests and the performance will be recorded, leading to the Hawthorne effect. Hawthorne effect stands for the tendency of some people to perform better when they know they are the participants in an experiment. The existence of the Hawthorne effect may cause students to change their behavior, such as trying to complete the test as soon as possible to achieve better performance, precisely because they know they are receiving research attention. Then, the results may be biassed and inaccurate.

**Sample Size:**
The sample size was the major limitation of this study. Large samples could have provided more reliable results.
Small sample size may cause a large standard deviation, which would lead the result to be less accurate and decreasingly representative of the entire population. Future research should expand sample size.

**Additional experimental materials:**
The study was conducted to test how background music affected participants' attention levels in two groups. In the within-subject design, the researcher would require to prepare two different Trail Making Test for each participant due to each student needs to test twice. For the control and treatment groups in the between-subject design, only one Trail Making Test was needed because each group only sees the material once. Therefore, using a within-subject design, the individual difference of participants is reduced but instead projects problems with individual differences between the materials participant are exposed to. The materials must therefore be carefully examined to ensure equal quality in factors such as difficulty.

### Next Steps
**Between-subject Design with different types of music:**
After expanding the sample size, change the experiment design to a between-subjects study experiment.  Between-subjects design means each participant will only test each situation once, which prevents practice effect by eliminating the transfer of knowledge and shorten testing sessions by allowing each participant only need to do the test once.

@@

**Stroop Test:**
Use Stroop Test^[The Stroop Color and Word Test (SCWT) is a neuropsychological test extensively used to assess the ability to inhibit cognitive interference that occurs when the processing of a specific stimulus feature impedes the simultaneous processing of a second stimulus attribute, well-known as the Stroop Effect[@stroop]] instead of Trail Making Test for the experiment to test student's cognitive ability with background music.The Stroop Test consisted of two parts, Stroop Color and Word Test. The participants require to identify the colour of the colour word. For example, the word green with the colour black, the tester should choose the answer black. The Stroop test could better reflect whether background music distracts student's attention level by displaying the speed of processing information.

>>>>

### The enjoyment of music will affect the completion time of the test
After completing two rounds of testing, participants were asked to rate the background music, 1 to 5 anonymously. The higher the score, represents the more they liked the song.  Regardless of the environment in which the test is completed, the overall average time for the 47 students participating in the experiment to complete a test is about 45 seconds. The result of visualizing the relationship between favourability and the rating shows that when the participants give a score greater than or equal to 3 out of 5, the average time to complete the test is less than the overall average completion time.  This situation illustrates that when students hear the background music they don’t like, their attention level is much lower than those who listen to background music they like.

### Interactive graphs on Shinyapp
In order to allow readers to have a more direct and diverse data exploration process, I drew a bar graph on shinyapp. The readers can check the distribution of the data according to the students' ratings of the background music, the gender of the students, and whether there is background music in the tests performed by the students so that you have a basic understanding of the data. The Shinyapp link for the interactive graphs is https://hongtrista.shinyapps.io/Shinyapp/?_ga=2.86381278.759236858.1619203106-1272735195.1619203106

@@

### Each student’s initial attention level is different
Before creating the linear mixed model, the model assumptions needed to be checked and the suitability of the model needed to be checked as well. The model assumptions are whether the variance of the residuals is equal across groups, whether the residuals of the model are normally distributed, and whether there does not exist multicollinearity. The plots shown in the Model Diagnostics subsection under the Model section show that all the assumptions being satisfied. When checking the linear mixed model fit the data collected from the experiment, the resulting plot shown in Figure \@ref(fig:randomeffect) demonstrates that each student's initial attention level is different and fixed effects will vary each student. In other words, the linear mixed model is suitable for this data and can incorporate student-to-student variability in finishing time and improve the ability to describe how fixed effects relate to outcome.

### Background music does not significantly affect the level of attention of students
The main research question for the paper is whether background music impacts student's attention level—two different types of analysis being conducted for the data, which are descriptive analysis and statistical analysis. From the descriptive analysis, the result shows that in the case of background music, the average time for students to complete the test is longer than that without background music. For the statistical analysis, five linear mixed models with different fixed effect terms and the same random effect term being created. The purpose is to find the most suitable model for the data. Comparing models using ANOVA and AIC shows that only a model with variable order is the best model. The variable Test_Type used to show whether the data was collected from a test with background music or not has no significant relationship with the attention level in the final model. Even in descriptive analysis, the results show that background music has a negative effect on students' attention level to a certain extent, but in a statistical sense, background music does not affect students' attention.

### The order of testing will affect the time to complete the test
After the procedure of model selection, the results show that the order significantly affects the time it takes for students to complete the test. In the final best-fit model, the coefficient of order is -10.65, and the 90% confidence interval is from -14.85 to -6.45. The coefficient, -10.65, means, on average, the time for completing the test in second-order is 10.65 seconds faster than the time in the first order when holding other variables constant.

@@

## Weaknesses
### Practice Effect
Each participant is measured for two conditions in the within-subject design(repeated measure design). Participants learn about the type and difficulty of the question when they take the Trail Making Test for the first time, so they may become more adept simply with the question and more proficient because of the repeated test, making the second-round test result more optimistic. In addition to the students' understanding of the test questions, some participants may feel bored or have a negative attitude to repeat the same test, making the results inaccurate.

### Hawthorn Effect
During the experiment, participants know that they are part of the experiment and observed. Their speed of doing the tests and the performance will be recorded, leading to the Hawthorne effect. Hawthorne effect stands for the tendency of some people to perform better when they know they are the participants in an experiment. The existence of the Hawthorne effect may cause students to change their behavior, such as trying to complete the test as soon as possible to achieve better performance, precisely because they know they are receiving research attention. Then, the results may be biassed and inaccurate.

### Sample Size
The primary limitation of the study is the small sample size. Large samples could have provided more reliable results. Simultaneously, the small number of participants established a deficient power level for the study, which provided a much smaller opportunity to achieve statistical significance. Small sample size may also cause a large standard deviation, which would lead the result to be less accurate and decreasingly representative of the entire population. Future research should expand the sample size.

### Additional experimental materials
The study was conducted to test how background music affected participants' attention levels in two groups. In the within-subject design, the researcher would require to prepare two different Trail Making Test for each participant due to each student needs to test twice. For the control and treatment groups in the between-subject design, only one Trail Making Test was needed because each group only sees the material once. Therefore, using a within-subject design, the individual difference of participants is reduced but instead projects problems with individual differences between the materials participant are exposed to. The materials must therefore be carefully examined to ensure equal quality in factors such as difficulty.

## Next Steps
### Between-subject Design with different types of music
After expanding the sample size, change the experiment design to a between-subjects study experiment.  Between-subjects design means each participant will only test each situation once, which prevents practice effect by eliminating the transfer of knowledge and shorten testing sessions by allowing each participant only need to do the test once.

@@

### Stroop Test
The Stroop test^[The Stroop Color and Word Test (SCWT) is a neuropsychological test extensively used to assess the ability to inhibit cognitive interference that occurs when the processing of a specific stimulus feature impedes the simultaneous processing of a second stimulus attribute, well-known as the Stroop Effect[@stroop]] consists of two parts: Stroop colour and Word test. Participants need to recognize the colour of words with colour properties. In other words, participants need to identify the colour of the font rather than the meaning of the colour represented by the word. For example, when the word is green but it appears in black, the participants need to answer black instead of green in the test. Students can be divided into different groups to do the Stroop test to study whether background music will distract students or study what type of background music is most likely to affect students' level of attention. The time taken by students to answer questions will be recorded as the speed at which the brain processes information, thereby inferring whether the attention is distracted.
